Summer 2025 ToDo

### 2025-10-22 Relations/Paper/Summer_2025_TODO.tex
WIP swapping control

\section*{September 15th todo}
\begin{todolist}
  \item (Minor) We want to have a sentence in our WF section making clear that we can consider local properties as well and maybe make an example from accessible to sequential. 
  \item Sentence explaining that wfacc is equivalent to wfind and therefore isn't included in the diagram (wfind).
  \item 
\end{todolist}

>>>>

\section*{September 15th todo}
\begin{todolist}
  \item (Minor) We want to have a sentence in our WF section making clear that we can consider local properties as well and maybe make an example from accessible to sequential. 
  \item Sentence explaining that wfacc is equivalent to wfind and therefore isn't included in the diagram (wfind).
\end{todolist}

\section*{September 26th TODO}
\begin{todolist}     
  \item Focus for next meeting on writing. 
  \item [\done] Are not not closed predicates over natural numbers dedcidable: If not is this a counterexample for WFminDNE.
\end{todolist}

\section*{October 10th TODO}
\begin{todolist}     
  \item Want to show that FB and weak decidability gives us accCor (think we may have shown this previously)
  \item Add 'is' to wfcor macros.
  \item make a decision on wfseq not not name. 
  \item Keep on cleaning the WF section in paper. 
  \item 
\end{todolist}

\section*{October 15th TODO}
\begin{todolist}     
  \item It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
  \item Do we want to keep anything in the old/delete section of WF?
  \item Do we want to add anything about counter examples or positive examples? 
  \item We may want to use words rather than macros in certain locations
  \item Check through the comments in general in the section. 
  \item 
\end{todolist}

### 2025-10-22 Relations/Paper/Well-foundedness.tex

>>>>

\begin{figure}[hb]
\centering  
\begin{tikzpicture}[
  scale=0.7,
  every node/.style={transform shape},
  node distance=1cm and .5cm,
  box/.style={draw, rectangle, rounded corners, minimum width=1cm, minimum height=1cm, align=center},
  arrow/.style={-{Latex}, thick}
]

% Row 1: WFmin -> WFmin-
\node[box] (WFmin) {$\WFmin$};
\node[box, right=2.9cm of WFmin] (WFminM) {$\WFminm$};

% Row 2: WFminDNE -> WFminDNE-
\node[box, below=of WFmin] (WFminDNE) {$\WFminDNE$};
\node[box, below=of WFminM] (WFminDNEM) {$\WFminDNEm$};

% Row 3: WFacc

\node[box, below=of WFminDNE] (WFacc) {$\WFacc$};

\node[box, below = of WFminDNEM] (WFaccM) {$\WFaccm$};
\draw[arrow, bend right] (WFacc) to (WFaccM);
\draw[arrow, bend right] (WFaccM) to node[below, text=red] {$\accDNE$} (WFacc);

% Row 4: WFseq
\node[box, below=of WFacc] (WFseq) {$\WFseq$};
\node[box, below= of WFaccM] (WFseqM) {$\WFseqm$};

% Row 5: WFcor 
\node[box, below=of WFseq] (WFCor) {$\WFcor$};
\node[box, below=of WFseqM] (WFminCor) {$\WFcorm$};

% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);

% Inter-row arrows
\draw[arrow] (WFacc) to node[right, text = red] {$\rdec$} (WFseq);
\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
\draw[arrow, bend right = 90] (WFminCor) to node[right, text=red] {$\accCor$} (WFaccM);

\draw[arrow, bend right = 90] (WFmin) to (WFseq);
\draw[arrow] (WFaccM) -- (WFseqM);
\draw[arrow] (WFmin) -- (WFminDNE);
\draw[arrow, bend right] (WFminM) to (WFminDNEM);
\draw[arrow, bend right] (WFminDNEM) to (WFminM);

\draw[arrow] (WFminDNE) to node[right, text = red] {$\accDNE$} (WFacc);
\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {$\mpe$} (WFseq);
\draw[arrow, bend right] (WFminDNEM) to node[left, text=red] {$\FB$} (WFaccM);
\draw[arrow, bend right] (WFseqM) to (WFminCor);
\draw[arrow, bend right] (WFminCor) to node [right, text=red] {$\mpe$} (WFseqM);
\draw[arrow] (WFCor) -- (WFminCor);
% \draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {$\accCor$} (WFacc);
\draw[arrow, bend left] (WFminCor) to node[below, text=red] {$\corDNE$} (WFCor);

\draw[arrow, dashed, bend left=80, blue] (WFCor) to node[left, text=blue] {$\accCor$} (WFacc);

\end{tikzpicture}
\caption{The logical relationships between notions of well-foundedness}
 \label{fig:WF2} 
\end{figure}
\clearpage
